Grip strength, mating success, and immune and energy costs in a population sample of US women and men: a registered report

### 2024-04-11 paper.qmd
Switched from color to bold

:::{#tbl-power}
```{r}
v <- ifelse(as.matrix(df_pwr[-1])>0.8, 'red', 'black')
tt(df_pwr) |>
  group_tt(j = list("Partnered" = 2:3, "Lifetime partners" = 4:5, "Last year partners" = 6:7)) |>
  format_tt(j = 1:7, digits = 2, num_zero = T) |>
  style_tt(j = 1:7, align = c("ccccccc")) |> 
  style_tt(i=1:4, j=2:7, color = v)
```

Power to detect strength and sex X strength coefficients that range from 25% to 100% of the size seen in the pilot study. **Scale**: the proportion of the effect seen in the pilot study. All other values are power (1-B). Values rounded to two significant digits. Red: power > 0.80.
:::

>>>>

:::{#tbl-power}
```{r}
v <- ifelse(as.matrix(df_pwr[-1])>0.8, T, F)
tt(df_pwr) |>
  group_tt(j = list("Partnered" = 2:3, "Lifetime partners" = 4:5, "Last year partners" = 6:7)) |>
  format_tt(j = 1:7, digits = 2, num_zero = T) |>
  style_tt(j = 1:7, align = c("ccccccc")) |> 
  style_tt(i=1:4, j=2:7, color = v)
```

Power to detect strength and sex X strength coefficients that range from 25% to 100% of the size seen in the pilot study. **Scale**: the proportion of the effect seen in the pilot study. All other values are power (1-B). Values rounded to two significant digits. Bold: power > 0.80.
:::
